Rapid-response Bayesian sky localization for electromagnetic follow-up of gravitational-wave candidates

### 2013-07-26 ms.tex
Make another sentence less formal

The likelihood, or the probability of obtaining the observation $\mathbf x$ conditioned on the value of $\boldsymbol\theta$, is Gaussian, with the log\nobreakdashes-likelihood proportional to:
%
\begin{equation}\label{eq:gaussian-likelihood}
	\mathcal{L}(\mathbf x; \boldsymbol\theta) = \prod_i p(x_i | \boldsymbol\theta)
		\propto \exp \left[
		- \frac{1}{2} \sum_i \int_0^\infty \frac{\left|x_i (\omega)
			- h_i(\omega; \boldsymbol\theta) \right|^2}{S_i(\omega)} \, \mathrm{d}\omega
	\right].
\end{equation}

>>>>

The likelihood, or the probability of obtaining the observation $\mathbf x$ conditioned on the value of $\boldsymbol\theta$, is the product of Gaussian distributions, one Gaussian for each detector:
%
\begin{equation}\label{eq:gaussian-likelihood}
	\mathcal{L}(\mathbf x; \boldsymbol\theta) = \prod_i p(x_i | \boldsymbol\theta)
		\propto \exp \left[
		- \frac{1}{2} \sum_i \int_0^\infty \frac{\left|x_i (\omega)
			- h_i(\omega; \boldsymbol\theta) \right|^2}{S_i(\omega)} \, \mathrm{d}\omega
	\right].
\end{equation}
